%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Igor} % Your first name
\familyname{Zarvanskiy} % Your last name

\address{Igor Zarvanskiy, 25 years}{Kiev, Ukraine}
\mobile{+38 (093) 307 5219}
\email{iclutcher@gmail.com}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\section{Summary of qualification}

\cvitem{Languages}{Java, PHP, python}
\cvitem{Databases}{MySQL, MongoDB}
\cvitem{VCS}{Mercurial, Git}
\cvitem{Dev. tools}{IntelliJ IDEA, PyCharm, PHPStorm, Eclipse, Sublime Text}
\cvitem{OS}{Linux, Windows}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2013--2015}{PhD Student}{
National Technical University of Ukraine ``Kyiv Polytechnic Institute''}{Educational-scientific complex ``Institute for applied system analysis'', Department of mathematical methods of system analysis}{Diploma thesis: Analysis of numerical series using graphs visibility methods to predict heart disease}{}
\cventry{2011--2013}{Masters of Applied mathematics}{National Technical University of Ukraine ``Kyiv Polytechnic Institute''}{Department of applied mathematics}{Diploma thesis: Model of complex web-networks with second-order phase transition}{}
\cventry{08.2012}{European Summer School in Industrial Mathematics 
and Modelling}{Technische Universitat Dresden}{}{}{}
\cventry{2007--2011}{Bachelor of Applied mathematics}{National Technical University of Ukraine ``Kyiv Polytechnic Institute''}{Department of applied mathematics}{Diploma thesis: Distributed expert-analytical system of POS sales and service}{}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Vocational}

\cventry{2015--Present}{Java/Hybris Developer}{\textsc{Skywind/Playtech}}{Kiev}{}{
Develop and support e-commerce project.
}
\cventry{2013--Present}{Python/PHP Developer}{\textsc{JayaDigital}}{Kiev}{}{
Dynamic web application programming and HTML coding using Symfony2 as framework.}
\cventry{2009--2014}{Web Developer}{Freelance}{Kiev}{}{Dynamic web site design and programming using CMS ``Drupal''.}

%------------------------------------------------

\subsection{Miscellaneous}

\cventry{2011--2013}{Director/Founder}{Kraftman Ukraine}{Kiev}{}{Managing director of printing  equipment distribution company.}
\cventry{2007--2013}{System Administator}{Vogt Medical Vertrieb GMBH}{Kiev}{}{Provide Windows/Linux administration, network operating center administration, LAN/WAN/VPN administration, intrusion detection and prevention monitoring. Also manage FTP servers, AD/DNS, wireless access points and load balancers. Design and implement highly available and disaster recovery solutions.}


%----------------------------------------------------------------------------------------
%	PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\cventry{2015--2016}{Keymaster}{}{}{}{
Description: web application for managing markers on map.\newline{}
Responsibilities: app full development, django, leaflet.js, angular\newline{}
}
\cventry{07.2014--2015}{CryptoCash}{}{}{}{
Description: Web App for electronic money exchange.\newline{}
Responsibilities: Symfony2 framework - defeloping multi-module system for electronic money exchange. Developed modules: APIBundle - integration Symfony2 framework with WebMoney, YandexMoney, Qiwi, PerfectMoney, Blockchain(Bitcoin), Privat24, OkPay, EgoPay; ExchangeProcessBundle - module responsible for exchange process workflow, LogBundle - module for logging based on events(Observer pattern). Designing and implementing server infrastructure on AWS. Process json and xml data.\newline{}
\emph{Site: https://cryptocash.co/}\newline{}
}
\cventry{08.2013--Present}{KPS}{}{}{}{
Description: Set of script for analizing cardiogram and make prediction about disease.\newline{}
Responsibilities: app full development, using cprofile to profile and icrease speed of app, process data in gpickle, xls, txt, math backgroud.\newline{}
Libraries: networkx, matplotlib\newline{}
}
\cventry{06.2014--07.2014}{Yaka}{}{}{}{
Description: Corporate site for cosmetics distribution.\newline{}
Responsibilities: Drupal 7 full app developing.\newline{}
\emph{Site: http://yaka.kiev.ua/}\newline{}
}
\cventry{05.2014--07.2014}{Tryton ERP research}{}{}{}{
Description: Research workflow of Tryton ERP-system. 
Responsibilities: research and documenting internal API of tryton.\newline{}
\emph{Publications: http://habrahabr.ru/post/222121}\newline{}
}
\cventry{03.2014--05.2014}{Map generator}{}{}{}{
Description: Script for generating random maps for iOS game (main idea of game - pathfinding).\newline{}
Responsibilities: app full development, process data in plist format, math backgroud.\newline{}
Libraries: networkx, matplotlib, PIL\newline{}
\emph{Source: https://bitbucket.org/clutcher/cng}\newline{}
}
\cventry{12.2013--04.2014}{AllUkraine}{}{}{}{
Description: Tourist catalog of Ukraine sightseeing.\newline{}
Responsibilities: Yii 1.1.14 framework - php views coding.\newline{}
}
\cventry{10.2013--12.2013}{Ailant}{}{}{}{
Description: Hotel recreation site.\newline{}
Responsibilities: Drupal 7 full app developing.\newline{}
\emph{Site: http://ailant.com.ua/}\newline{}
}
\cventry{04.2013--12.2013}{X-Rift}{}{}{}{
Description: Augmented reality game for android.\newline{}
Responsibilities: Designing and implementing server infrastructure, restful api service and monster AI.\newline{}
Libraries: pymongo, flask, requests, threading\newline{}
}
\cventry{05.2013--06.2013}{EnlNexus}{}{}{}{
Description: Android app for notification about Ingress game process.\newline{}
Responsibilities: Designing and implemeting server infrastructure, parsing ingress.com/intel, process json data.\newline{}
Libraries: pymongo, flask, requests\newline{}
\emph{Source: https://bitbucket.org/clutcher/enlnexus}\newline{}
}
\cventry{11.2012--01.2013}{PMT}{}{}{}{
Descriptions: set of scripts for calculating the strength of the pipes with defects.\newline{} 
Responsibilities: app full development, math backgroud, making edits in Ukraine State Standards.\newline{}
\emph{Source: https://bitbucket.org/clutcher/pmt}\newline{}
}
\cventry{03.2012--01.2013}{NRT}{}{}{}{
Description: Set of tools for modeling and analyzing complex networks.\newline{}
Responsibilities: app full development, math background.\newline{}
Libraries: networkx , pyqt, matplotlib\newline{}
\emph{Source: https://bitbucket.org/clutcher/nrt}\newline{}
}
\cventry{7.2011--10.2013}{Kraftman}{}{}{}{
Description: Corporate site for printing equipment distribution.\newline{}
Responsibilities: Drupal 7 full app developing.\newline{}
\emph{Site: http://kraftman.com.ua/}\newline{}
}

%----------------------------------------------------------------------------------------
%	AWARD SECTION
%----------------------------------------------------------------------------------------

% \section{Awards}

% \cvitem{2011}{School of Business Postgraduate Scholarship}
% \cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Russian}{Native}{}
\cvitemwithcomment{Ukraine}{Native}{}
\cvitemwithcomment{English}{Intermediate}{}

\end{document}