%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Igor} % Your first name
\familyname{Zarvanskyi} % Your last name

\address{Igor Zarvanskyi}{Valencia, Spain}
%\mobile{+38 (093) 307 5219}
%\email{iclutcher@gmail.com}
\homepage{Linkedin}{https://www.linkedin.com/in/igor-zarvanskyi}
\extrainfo{Personal blog: \href{https://clutcher.github.io}{https://clutcher.github.io}}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

    \makecvtitle{
        Software Architect and Development Manager with over fifteen years of progressive experience producing a range of software solutions through the entire product life-cycle. Currently I`m focused on designing, creating and giving support to SAP Commerce solutions.} % Print the CV title


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

    \section{Experience}

    \subsection{Vocational}
    \cventry{2019--now}{Software Architect/Dev. Manager (Java/SAP Commerce)}{Zaelab}{}{}{
        Started working in company as Senior Software Engineer was promoted to Software Architect and Dev. Manager. Managed teams from 4 to 25 people.
        \begin{itemize}
            \item {Swagelok}\newline{}
            \emph{Description:} Industrial fluid systems selling e-commerce B2C/B2B site.\newline{}
            \emph{Technology stack:} java, MySQL, SAP Commerce Cloud, spring, jsp.\newline{}
            \emph{Responsibilities:}
            \begin{itemize}
                \item As Software Architect: designed architecture of combined search experience. Introduced technical documentation processes. Facilitate migration on SAP Commerce 2211. Introduced usage of patch framework. Improved ant build time to make it 2x faster.
                \item As Development Manager: lead team of 4 people. Introduced process of ticket prioritization, analysis and assignment. Introduced board in Azure DevOps to manage current work assignments and progress.
            \end{itemize}
            \item {Trek Bicycle}\newline{}
            \emph{Description:} Bicycles and apparel selling e-commerce B2C/B2B sites.\newline{}
            \emph{Technology stack:} java, MSSQL, SAP Commerce Cloud, spring, jsp, Vue.js.\newline{}
            \emph{Responsibilities:}
            \begin{itemize}
                \item As Software Architect: designed architecture of payment providers integrations. Rearchitectured B2B checkout process and cart model, designed architecture to allow selection of delivery mode(shipping) on cart entry level. Facilitate migration to SAP Commerce Cloud. Introduced documentation processes.
                \item As Development Manager: lead team of 25 people. Developed project plans and timelines. Coordinated with different teams to ensure project milestones are met. Monitored progress and made adjustments as necessary to keep projects on track. Allocated resources effectively to ensure projects are adequately staffed and resourced.
                \item As Developer: improved PDP page load speed from 6 sec to 50ms. Improved SAP Commerce startup time from 10 min to 6 min. Improved SAP Commerce build time from 5 min to 2 min. Refactored solr search customizations to work in non legacy mode. Integrated SAP Gigya SSO.
            \end{itemize}
        \end{itemize}
    }
    \cventry{2018--2019}{Technical Lead (Java/Hybris)}{Optaros}{}{1 year}{
        B2B project for Clarks with multi-country support.
        \begin{itemize}
            \item {Clarks}\newline{}
            \emph{Description:} Shoes selling e-commerce B2B site.\newline{}
            \emph{Technology stack:} java, mysql, hybris, datahub, spring, jsp, ES6.\newline{}
            \emph{Responsibilities:}
            \begin{itemize}
                \item As Tech Lead: lead the technical direction during design and development processes by driving decisions and coordinating efforts. Provided guidance to Hybris developers during design, development and implementation of features. Provided insights and guidance to internal and external stakeholders to demonstrate how the Hybris solution can be leveraged to meet business requirements. Analyzed business and IT challenges and designed a comprehensive solutions that integrates smoothly. Provided implementation expertise in how best to implement and use Hybris, identified scope gaps, advised on workaround solutions when applicable. Designed and implemented integration with 3rd party systems including legacy backend applications (SAP). Introduced TDD approach inside team. Established CI/CD pipeline and CI monitoring tools including SonarQube.
                \item As Developer: initial B2B project setup. Added multi-country support including product and CMS component user segmentation based on personalization module. Implemented master data exchange between hybris and SAP via datahub. Setup of order fulfillment process with order processing RFC to SAP. Integrated webpack into build system.
            \end{itemize}
        \end{itemize}
    }
    \cventry{2015--2018}{Software Engineer/Team Lead (Java/Hybris)}{Everything5pounds}{}{(3 years)}{
        Started working in company as Java Developer on big e-commerce project(B2C) made on Hybris platform, was promoted to Team Lead. Build team of 6 developers from scratch.
        \begin{itemize}
            \item {Everything5pounds}\newline{}
            \emph{Description:} Apparel selling e-commerce website with up to 40k simultaneous users and 3 mil pounds revenue per month.\newline{}
            \emph{Technology stack:} java, mysql, hybris, spring, jsp, angular1.\newline{}
            \emph{Responsibilities:}
            \begin{itemize}
                \item As Team Lead: introduced TDD approach inside team. Established CI and CI monitoring tools including Sonar scanner checks. Performed peer review for development team. Provided support in detailed project planning activities, daily scrum, code review and deadline management. Developed tool for measuring developers and team productivity. Contributed to design systems architecture, execute business logic and support functions. Made valuable contribution in switching deployment system to Docker.
                \item As Developer: implemented session storing in Hybris, implemented system for product feed generating for different consumers, implemented integration with commerce hub, bronto, Paypal, safecharge. Provided migrations from Hybris 5.3 up to Hybris 6.5. Configured solr search servers. Remade hybris default order/consignment processes. Developed API for Whitelabel integration. Implemented social login. Improved Backoffice commerce search widgets.
            \end{itemize}
        \end{itemize}
    }

%------------------------------------------------

    \subsection{Miscellaneous}

    \cventry{2013--2015}{Software Engineer (PHP)}{JayaDigital}{}{(2 years)}{
        \emph{Description:} Bug fixing and full support of existing systems based on Magento. Developed web application for electronic money exchange on symfony2.\newline{}
        \emph{Technology stack:} php5, mysql, symfony2, composer, twig.\newline{}
    }
    \cventry{2007--2014}{Software Engineer (PHP)}{Freelance}{}{(7 years)}{
        \emph{Description:} Developed more than 50 dynamic web sites in different areas: e-commerce, social networks, corporate sites etc.\newline{}
        \emph{Technology stack:} php5, mysql, Drupal 6/7, jquery.\newline{}
    }
    \cventry{2007--2014}{System Network Administrator}{Vogt Medical Vertrieb GMBH}{}{(7 years)}{Provide Windows/Linux administration, network operating center administration, LAN/WAN/VPN administration, intrusion detection and prevention monitoring. Also manage FTP servers, AD/DNS, wireless access points and load balancers. Design and implement highly available and disaster recovery solutions.}

%----------------------------------------------------------------------------------------
%	CERTIFICATION SECTION
%----------------------------------------------------------------------------------------


    \section{Certifications}

    \cventry{2022}{Software Design and Architecture Specialization}{Coursera}{}{\href{https://coursera.org/share/6680652d0e1056db914b917d789b1f1e}{verify certificate}
    }{}
%    \cventry{2020}{Enterprise Design Thinking Practitioner}{IBM}{}{\href{https://www.credly.com/badges/16c70702-33e6-48b7-ac22-d98ae5bd47a0}{verify certificate}
%    }{}
    \cventry{2020}{Reactive Architecture: Advanced}{IBM}{}{\href{https://www.credly.com/badges/0e7f8a5a-5286-4694-829c-7731598f306e}{verify certificate}
    }{}
    \cventry{2020}{Professional Scrum Product Owner I}{Scrum.org}{}{\href{https://www.scrum.org/certificates/526339}{verify certificate}
    }{}
    \cventry{2019}{SAP Commerce Cloud 6.7 Developer}{SAP}{}{\href{https://www.credly.com/badges/984a5872-00c0-492a-852f-716808af3df2}{verify certificate}
    }{}
    \cventry{2018}{SAP Hybris Commerce 6.2}{SAP}{}{\href{https://www.credly.com/badges/99506246-2cd6-4ca0-8e08-c61cb2942f70}{verify certificate}
    }{}





%----------------------------------------------------------------------------------------
%	PET PROJECTS SECTION
%----------------------------------------------------------------------------------------


    \section{Pet projects}

    \cventry{2019--now}{Better Highlights}{}{}{(5 years)}{
        \emph{Description:} Intellij IDEA plugin to highlight code comments, reference source code from comments and show cognitive complexity.\newline{}
        \emph{Technology stack:} java.\newline{}
        \emph{Responsibilities:} plugin full development.\newline{}
        \emph{Homepage:} \href{https://plugins.jetbrains.com/plugin/12895-comments-highlighter}{Link to plugin}.
    }

\end{document}