%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Igor} % Your first name
\familyname{Zarvanskyi} % Your last name

\address{Igor Zarvanskyi}{Kyiv, Ukraine}
%\mobile{+38 (093) 307 5219}
%\email{iclutcher@gmail.com}
\homepage{Linkedin}{https://www.linkedin.com/in/igor-zarvanskyi}
\extrainfo{Personal Hybris blog: \href{https://clutcher.github.io}{https://clutcher.github.io}}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

    \makecvtitle{
    Technical Lead with over ten years of progressive experience producing a range of software solutions through the entire product life-cycle. Currently I`m focused on designing, creating and giving support to Hybris e-commerce solutions.} % Print the CV title
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------


%    \section{Summary of qualification}
%
%    \cvitem{Languages}{Java, Python}
%    \cvitem{Databases}{MySQL, PostgreSQL, Redis}
%    \cvitem{Frameworks}{Java: Hybris 5.3-2005, Spring; Python: Django}
%    \cvitem{Technologies}{Tomcat, Apache Solr, AWS, Docker, Git}

%----------------------------------------------------------------------------------------
%	CERTIFICATION SECTION
%----------------------------------------------------------------------------------------


    \section{Certifications}

    \cventry{2020}{Enterprise Design Thinking Practitioner}{IBM}{}{\href{https://www.youracclaim.com/badges/16c70702-33e6-48b7-ac22-d98ae5bd47a0}{verify certificate}
    }{}
%    \cventry{2020}{Reactive Architecture Foundations}{IBM}{}{\href{https://www.youracclaim.com/badges/838c50eb-eca8-4f6e-8db7-128506f887bf}{verify certificate}
%    }{}
    \cventry{2020}{Professional Scrum Product Owner I}{Scrum.org}{}{\href{https://www.scrum.org/certificates/526339}{verify certificate}
    }{}
    \cventry{2019}{SAP Commerce Cloud 6.7 Developer}{SAP}{}{\href{https://www.youracclaim.com/badges/a6b20550-7844-45f4-9d08-ef74a122a9ba}{verify certificate}
    }{}
    \cventry{2018}{SAP Hybris Commerce 6.2}{SAP}{}{\href{https://www.youracclaim.com/badges/55da060d-fb04-4d6a-b8e3-5073b1452b06}{verify certificate}
    }{}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


    \section{Experience}

    \subsection{Vocational}
    \cventry{2019--now}{Senior Software Engineer (Java/Hybris)}{\textsc{Zaelab}}{Kyiv}{}{
    Optimizations for B2C/B2B projects for Trek Bicycles.
    \begin{itemize}
        \item {Trek Bicycle}\newline{}
        \emph{Description:} Bicycles and apparel selling e-commerce B2B/B2C sites.\newline{}
        \emph{Technology stack:} java, MSSQL, hybris, spring, jsp, Vue.js.\newline{}
        \emph{Responsibilities:}
        \begin{itemize}
            \item As Developer: improved PDP page load speed from 6 sec to 50ms. Improved Hybris startup time from 10 min to 6 min. Improved Hybris build time from 5 min to 2 min. Refactored solr search customizations to work in non legacy mode. Integrated SAP Gigya SSO.
        \end{itemize}
    \end{itemize}
    }
    \cventry{2018--2019}{Technical Lead (Java/Hybris)}{\textsc{Optaros}}{Kyiv}{1 year}{
    B2B project for Clarks with multi-country support.
    \begin{itemize}
        \item {Clarks}\newline{}
        \emph{Description:} Shoes selling e-commerce B2B site.\newline{}
        \emph{Technology stack:} java, mysql, hybris, datahub, spring, jsp, ES6.\newline{}
        \emph{Responsibilities:}
        \begin{itemize}
            \item As Tech Lead: lead the technical direction during design and development processes by driving decisions and coordinating efforts. Provided guidance to Hybris developers during design, development and implementation of features. Created interface designs and high-level solution designs. Provided insights and guidance to internal and external stakeholders to demonstrate how the Hybris solution can be leveraged to meet business requirements. Analyzed business and IT challenges and designed a comprehensive solutions that integrates smoothly. Provided implementation expertise in how best to implement and use Hybris, identified scope gaps, advised on workaround solutions when applicable. Designed and implemented integration with 3rd party systems including legacy backend applications (SAP). Introduced TDD approach inside team. Established CI/CD pipeline and CI monitoring tools including SonarQube.
            \item As Developer: initial B2B project setup. Added multi-country support including product and CMS component user segmentation based on personalization module. Implemented master data exchange between hybris and SAP via datahub. Setup of order fulfillment process with order processing RFC to SAP. Integrated webpack into build system.
        \end{itemize}
    \end{itemize}
    }
    \cventry{2015--2018}{Software Engineer/Team Lead (Java/Hybris)}{\textsc{Everything5pounds}}{Kyiv}{(3 years)}{
    Started working in company as Java Developer on big e-commerce project(B2C) made on Hybris platform, was promoted to Team Lead. Build team of 6 developers from scratch.
    \begin{itemize}
        \item {Everything5pounds}\newline{}
        \emph{Description:} Apparel selling e-commerce web site with up to 40k simultaneous users and 3 mil pounds revenue per month.\newline{}
        \emph{Technology stack:} java, mysql, hybris, spring, jsp, angular1.\newline{}
        \emph{Responsibilities:}
        \begin{itemize}
            \item As Team Lead: introduced TDD approach inside team. Established CI and CI monitoring tools including Sonar scanner checks. Performed peer review for development team. Provided support in detailed project planning activities, daily scrum, code review and deadline management. Developed tool for measuring developers and team productivity. Contributed to design systems architecture, execute business logic and support functions. Made valuable contribution in switching deployment system to Docker.
            \item As Developer: implemeted session storing in Hybris, implemented system for product feed generating for different consumers, implemented integration with commerce hub, bronto, paypal, safecharge. Provided migrations from Hybris 5.3 up to Hybris 6.5. Configured solr search servers. Remade hybris default order/consignment processes. Developed API for Whitelabel integration. Implemented social login. Improved Backoffice commerce search widgets.
        \end{itemize}
    \end{itemize}
    }

%------------------------------------------------

    \subsection{Miscellaneous}

    \cventry{2013--2015}{Software Engineer (PHP)}{\textsc{JayaDigital}}{Kyiv}{(2 years)}{
    \emph{Description:} Bug fixing and full support of existing systems based on Magento. Developed web application for electronic money exchange on symfony2.\newline{}
    \emph{Technology stack:} php5, mysql, symfony2, composer, twig.\newline{}
    \emph{Responsibilities:} developed multi-module system for electronic money exchange. Implemented integrations with WebMoney, YandexMoney, Qiwi, PerfectMoney, Blockchain(Bitcoin), Privat24, OkPay, EgoPay. Designed and developed exchange process workflow. Designed and implemented server infrastructure on AWS.
    }
    \cventry{2007--2014}{Software Engineer (PHP)}{\textsc{Freelance}}{Kyiv}{(7 years)}{
    \emph{Description:} Developed more than 50 dynamic web sites in different areas: e-commerce, social networks, corporate sites etc.\newline{}
    \emph{Technology stack:} php5, mysql, Drupal 6/7, jquery.\newline{}
    \emph{Responsibilities:} full app development.
    }
    \cventry{2007--2014}{System Network Administrator}{Vogt Medical Vertrieb GMBH}{Kyiv}{(7 years)}{Provide Windows/Linux administration, network operating center administration, LAN/WAN/VPN administration, intrusion detection and prevention monitoring. Also manage FTP servers, AD/DNS, wireless access points and load balancers. Design and implement highly available and disaster recovery solutions.}

%----------------------------------------------------------------------------------------
%	PET PROJECTS SECTION
%----------------------------------------------------------------------------------------


    \section{Pet projects}

    \cventry{2019--now}{Comments Highlighter}{}{}{(1 year)}{
    \emph{Description:} Intellij IDEA plugin to highlight code comments.\newline{}
    \emph{Technology stack:} java.\newline{}
    \emph{Responsibilities:} plugin full development.\newline{}
    \emph{Homepage:} \href{https://plugins.jetbrains.com/plugin/12895-comments-highlighter}{Link to plugin}.
    }
    \cventry{2016--2018}{Metrics}{}{}{(2 years)}{
    \emph{Description:} web application for measuring developers productivity, calculate estimations, make prediction about release dates, combine release notes, CI monitor.\newline{}
    \emph{Technology stack:} python3, django, python-jira, python-bitbucket.\newline{}
    \emph{Responsibilities:} app full development.
    }
%    \cventry{2015--2017}{Keymaster}{}{}{(2 years)}{
%    \emph{Description:} web application for route planning and managing markers on map.\newline{}
%    \emph{Technology stack:} python3, postgresql, django, DRF, leaflet.js, angular.\newline{}
%    \emph{Responsibilities:} app full development.
%    }
% \cventry{2012--2015}{KPS}{}{}{(3 years)}{
%     \emph{Description:} Set of script for analizing cardiogram and make disease prediction.\newline{}
%     \emph{Technology stack:} python2, networkx, matplotlib\newline{}
%     \emph{Responsibilities:} app full development, using cprofile to profile and icrease speed of app, process data in gpickle, xls, txt, math backgroud.
% }

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


%    \section{Education}
%
%    \cventry{2013--2015}{PhD Student}{National Technical University of Ukraine ``Kyiv Polytechnic Institute''}{Educational-scientific complex ``Institute for applied system analysis'', Department of mathematical methods of system analysis}{}{}
%    \cventry{08.2012}{European Summer School in Industrial Mathematics and Modelling}{Technische Universitat Dresden}{}{}{}
%    \cventry{2007--2013}{Masters of Applied mathematics}{National Technical University of Ukraine ``Kyiv Polytechnic Institute''}{Department of applied mathematics}{}{}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------


%    \section{Languages}
%
%%    \renewcommand{\listitemsymbol}{~} % Changes the symbol used for lists
%
%%    \cvlistdoubleitem{\cvitemwithcomment{English}{Intermediate}{}}{\cvitemwithcomment{Russian}{Native}{}}
%%    \cvlistdoubleitem{\cvitemwithcomment{Romanian}{Elementary}{}}{\cvitemwithcomment{Ukraine}{Native}{}}
%
%    \cvitemwithcomment{Russian}{Native}{}
%    \cvitemwithcomment{Ukraine}{Native}{}
%    \cvitemwithcomment{English}{Intermediate}{}
%    \cvitemwithcomment{Romanian}{Elementary}{}
\end{document}